The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-10-15 paper/authors.tex
acks
pretend DESC is an author

\author[0000-0001-7363-7932]{Angus H. Wright}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

@@

\author[0000-0002-4598-9719]{David Alonso}
\affiliation{Astrophysics, University of Oxford, DWB, Keble Road, Oxford OX1 3RH, UK}

@@

\author{Andrina Nicola}
\affiliation{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA}

@@

\collaboration{1000}{The LSST Dark Energy Science Collaboration (LSST DESC)}
\noaffiliation

>>>>

\author[0000-0001-7363-7932]{Angus H. Wright}
\affiliation{German Centre of Cosmological Lensing, Ruhr-Universit\"{a}t, Universit\"{a}tsstra{\ss}e 150, 44801 Bochum, Germany}

@@

\author[0000-0002-4598-9719]{David Alonso}
\affiliation{Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK}

@@

\author[0000-0003-2792-6252]{Andrina Nicola}
\affiliation{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA}

@@

\author{The LSST Dark Energy Science Collaboration (LSST DESC)}
\noaffiliation

### 2021-10-15 paper/paper.tex

\begin{document}
\title{The LSST-DESC 3x2pt Tomography Optimization Challenge}
\input{authors2}

@@

Authors CRB, ESC, BMOF, EJG, and GT are collaborators from outside the
Dark Energy Science Collaboration included here under a DESC publication policy exemption.

>>>>

\begin{document}
\title{The LSST-DESC 3x2pt Tomography Optimization Challenge}
\input{authors2}
\footnote{Author affiliations may be found before the references.}

@@

Authors CRB, ESC, BMOF, EJG, and GT are collaborators from outside the
Dark Energy Science Collaboration included here under a DESC publication policy exemption.
\vspace{1cm}

\subsection{Author Affiliations}

$^{1}$Institute for Astronomy, University of Edinburgh, Edinburgh EH9 3HJ, United Kingdom\\
$^{2}$AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France\\
$^{3}$German Centre of Cosmological Lensing, Ruhr-Universit\"{a}t, Universit\"{a}tsstra{\ss}e 150, 44801 Bochum, Germany\\
$^{4}$Brookhaven National Laboratory, Upton NY 11973, USA\\
$^{5}$Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA\\
$^{6}$Astrophysics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
$^{7}$Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud 150, 22290-180 Rio de Janeiro, RJ, Brazil\\
$^{8}$Centro Federal de Educa\c{c}\~{a}o Tecnol\'{o}gica Celso Suckow da Fonseca, Rodovia M\'{a}rcio Covas, lote J2, quadra J - Itagua\'{i} (Brazil)\\
$^{9}$INAF - Osservatorio Astronomico di Capodimonte, via Moiariello 16, I-80131, Napoli Italy\\
$^{10}$Department of Physics and Astronomy, Rutgers, the State University, Piscataway, NJ 08854, USA\\
$^{11}$Universit\'e Paris-Saclay, CNRS/IN2P3, IJCLab, 91405 Orsay, France\\
$^{12}$INFN - Sezione di Napoli, via Cinthia 21, I-80126 Napoli, Italy\\
$^{13}$Department of Physics ``E. Pancini'', University of Naples Federico II, via Cintia, 21, I-80126 Napoli, Italy\\
$^{14}$Universidade de S\~ao Paulo, IAG, Rua do Mat\~ao 1225, S\~ao Paulo, SP, Brazil\\
$^{15}$Instituto de Astronom\'{\i}a Te\'orica y Experimental (IATE-CONICET), Laprida 854, X5000BGR, C\'ordoba, Argentina.\\
$^{16}$Observatorio Astron\'omico de C\'ordoba, Universidad Nacional de C\'ordoba, Laprida 854, X5000BGR, C\'ordoba, Argentina.\\
$^{17}$Dunlap Institute for Astronomy and Astrophysics, University of Toronto, 50 St George St, Toronto, ON M5S 3H4, Canada\\
$^{18}$Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
$^{19}$Department of Physics and Astronomy, University of California, Davis, Davis, CA 95616, USA\\
$^{20}$Argonne National Laboratory, 9700 S Cass Ave, Lemont, IL 60439, USA\\
$^{21}$Department of Physics and Astronomy, Rutgers University, Piscataway, NJ 08854, USA
